---
title: "Quiz - Module 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. What is the correct mean and median of the coefficient of variations of the sales in the SKU dataset (DATA_2.01_SKU.csv)?

```{r}
data <- read.table('DATA_2.01_SKU.csv', header = T, sep = ',')
summary(data)
```

## 2. Do a hierarchical clustering on scaled data using an Euclidian distance and Ward.D clustering on the SKU dataset (DATA_2.01_SKU.csv). What are the resulting segments compared to what is shown in class if you decide to take only 2 clusters?

```{r}
plot(data$CV, data$ADS, main = 'SKU Example', ylab = 'Average Daily Sales', xlab = 'Coefficient of variation')
abline(v=0.2, col='red')
abline(h=4, col='red')
text(0.15, 9.7, 'horses', col='red')
text(0.65, 9, 'Wild Bulls', col = 'red')
text(0.8, 2, 'Crickets', col='red')
```

```{r}
testdata <- data
testdata <- scale(testdata)
d <- dist(testdata, method = 'euclidean')
hcward <- hclust(d, method='ward.D')
data$groups <- cutree(hcward, k=3)
library(lattice)
xyplot(ADS~ CV,main = "After 3 Clustering", type="p",group=groups,data=data,
       auto.key=list(title="Group", space = "left", cex=1.0, just = 0.95), 
       par.settings = list(superpose.line=list(pch = 0:18, cex=1)),
       col=c('blue','green','red'))
```

```{r}
data$groups <- cutree(hcward, k=2)
xyplot(ADS~ CV,main = "After 2 Clustering", type="p",group=groups,data=data,
       auto.key=list(title="Group", space = "left", cex=1.0, just = 0.95), 
       par.settings = list(superpose.line=list(pch = 0:18, cex=1)),
       col=c('blue','green','red'))
```

## 3. Which of the following graphs reports the correct plot of the last project evaluation as a function of the number of projects done for the HR dataset (DATA_2.02_HR.csv)?

```{r}
data <- read.table('DATA_2.02_HR.csv', header=T, sep=',')
plot(data$LPE, data$NP)
```

## 4. If you cluster the HR dataset (DATA_2.02_HR.csv) on Satisfaction, Project Evaluation and Number of Projects Done and that you keep 2 segments using the same values for the other specifications (scaling, distance type and clustering algorithm), what’s the resulting median Satisfaction per segment?

```{r}
testdata <- data[, 1:3]
testdata <- scale(testdata)
d = dist(testdata, method = 'euclidean')
hcward <- hclust(d, method = 'ward.D')
data$groups <- cutree(hcward, k=2)
aggdata = aggregate(.~ groups, data=data, FUN=median)
proptemp=aggregate(S~ groups, data=data, FUN=length)
aggdata$proportion=(proptemp$S)/sum(proptemp$S)
aggdata=aggdata[order(aggdata$proportion,decreasing=T),]
aggdata
```
