---
title: "Recital M3-HR example"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
datatot=read.table('DATA_3.02_HR2.csv', header = T,sep=',')
```

```{r}
str(datatot)
summary(datatot)
```

```{r}
# look at the frequencies for the left variable
table(datatot$left)
```

```{r}
# look at percentages for the left variable
table(datatot$left)/nrow(datatot)
```

```{r}
# alternatively, plot a histogram
hist(datatot$left)
```

```{r}
# Check out the correlations
cor(datatot)
```

```{r}
# Estimate the drivers of attrition
logreg = glm(left ~ ., family=binomial(logit), data=datatot)
```

```{r}
# See the proportion of employee attrition according to the model
hist(logreg$fitted.values)
```

```{r}
# Assess the correlation between estimated attrition and actual
cor(logreg$fitted.values, datatot$left)
```

```{r}
# Cutoff to determine when P[leaving] should be considered as a leaver or not
cutoff=0.3
```

```{r}
table(logreg$fitted.values>=cutoff, datatot$left)
```


```{r}
# Compute the percentage of correctly classified employees who stayed
sum((logreg$fitted.values<=cutoff)&(datatot$left==0))/sum(datatot$left==0)
# Compute the percentage of correctly classified employees who left
sum((logreg$fitted.values > cutoff)&(datatot$left==1))/sum(datatot$left==1)
# Compute the overall percentage of correctly classified employees
mean((logreg$fitted.values>cutoff)==(datatot$left==1))
```

```{r}
# Report the results of the logistic regression
summary(logreg)
```

```{r}
# Let's use a more visual way to see the effect of one of the most important driver: TIC
plot(datatot$TIC, datatot$left, main= "Time and Employee Attrition", ylab="Attrition", xlab= "Time spent")
```

```{r}
# An aggregated plot
tempdata <- datatot
# We compute the average attrition rate for each value of TIC
aggbTimeRank <- aggregate(left~ TIC, data = tempdata, FUN = mean)
plot(aggbTimeRank$TIC, aggbTimeRank$left, main= "Time and Employee Attrition", ylab="Average Attrition Rate", xlab= "Time spent")
```

An even better one!

```{r}
# We compute the number of employees for each value of TIC
cntbTimeRank=aggregate(left~ TIC, data=tempdata, FUN=length)
symbols(aggbTimeRank$TIC,aggbTimeRank$left,circles=cntbTimeRank$left, inches=.75, fg="white", bg="red",main= "Time and Employee Attrition", ylab="Average Attrition Rate", xlab= "Time spent")
```

Human perceive area of shapes like circles. So if some value is twice as large, we want the area of the circle to be twice as large, not the radius. The symbols() function takes the radius of the circles by default, so we need to compute the radius in order to end up with the desired size of circles.

```{r}
size = cntbTimeRank$left

radius = sqrt(size / pi)

symbols(x = aggbTimeRank$TIC, y = aggbTimeRank$left,

        circles = radius, inches = .75, fg = "white", bg = "red",

        main =  "Time and Employee Attrition",

        ylab = "Average Attrition Rate", xlab =  "Time spent")
```

Let's use a visual way to see the effect of the most important driver: Satisfaction

```{r}
tempdata <- datatot
# We create categories of employee satisfaction ranking. We create 20 groups (because it will work well later...)
tempdata$rankSatis = round(rank(-tempdata$S)/600)
# We compute the average attrition rate for each category
aggbSatisRank = aggregate(left~ rankSatis, data=tempdata, FUN=mean)
# We compute the number of employees for each value of TIC
cntbSatisRank = aggregate(left~ rankSatis, data=tempdata, FUN=length)
#Visualization
symbols(aggbSatisRank$rankSatis,aggbSatisRank$left,circles=cntbSatisRank$left, inches=.2, fg="white", bg="red",main= "Satisfaction and Employee Attrition", ylab="Average Attrition Rate", xlab= "Rank of Satisfaction")
```

Instead of creating roughly equal size groups of 20 by rank, we create 20 bins of equal size between 0 and 1 and assign each employee to 1 bin based on Satisfaction.

```{r}
bins = 20

breakPoints = seq(0, 1, length.out = (bins+1))

tempdata$rankSatis = (bins+1) - as.numeric(cut(tempdata$S, breaks = breakPoints))
```

Visually, these are the bins we are choosing:

```{r}
hist(tempdata$S, breaks = breakPoints)

abline(v = breakPoints, col = "red", lty = 2)
```

Note that the first bin 0-0.05 has no employees (so the circle should be size 0)

```{r}
# We compute the average attrition rate for each category
aggbSatisRank <- aggregate(left~ rankSatis, data = tempdata, FUN = mean)
# We compute the number of employees for each value of TIC
cntbSatisRank <- aggregate(left~ rankSatis, data = tempdata, FUN = length)

## Again here, we want to size the circles by their area, not radius
size <- cntbSatisRank$left

radius <- sqrt(size / pi)

symbols(x = aggbSatisRank$rankSatis, y = aggbSatisRank$left,

        circles = radius, inches = 0.2, fg = "white", bg = "red",

        main =  "Satisfaction and Employee Attrition",

        ylab = "Average Attrition Rate", xlab =  "Rank of Satisfaction")
```
